%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Acknowledgments}

I want like to express deepest appreciation to my supervisors, Prof. Andr\'e Ivanov and Prof. Karthik Pattabiraman, for their invaluable guidance that helped me to shape my research, and for their persistent encouragement and patience that made me fulfill my master's program.




%To my supervisor Andr\'e Ivanov, I would love to express my heartfelt gratitude to you for encouraging me to develop and grow as a researcher through your supports and our mindful discussions. It was an excellent opportunity to work in one of a kind research groups with such broad research areas.

I acknowledge our research group members, especially Mehdi Karimibiuki, who helped me tremendously via his feedback and comments. Also, I am gratefully thankful to all my passionate lab mates at the System On Chip and Dependable Systems laboratory.

I appreciate Natural Sciences and Engineering Research Council of Canada (NSERC) and Intel for providing the infrastructure and computational resources for conducting this project.

%I would like to express my profound appreciation to my best friends who accompanied and supported me with their love, encouragements, and their great friendship throughout my time in the graduate school; Hamid Etebarian, Amin Sadeghi, Amirhossein Salimian, and Pouya Aein. To my best friends, far and in different time zones, Sahand Asgharieh, Amirhossein Hemmati, and Moe Hamedi; I appreciate you for the continued and boundless support, enthusiasm, and dedication. Also, I would like to offer my special thanks to my dear friends, Navid Hanachi, Hatef Rahmani, and Harmun Sehmby for all their help, support, and empathy during these two years. 

Finally, I would like to express my gratitude towards my family without whom I wouldn't be able to complete this program. I thank my husband, Anuj Issar, for his whole-hearted and unconditional support, sacrifice, guidance, and dedication. My parents, Aggarwals and Sharmas, for sticking with me through thick and thin and constantly encouraging me. Finally my brother, Akshit Aggarwal, who through his constant nudging helped me to maintain calm and think with a clear head. I am delighted to have all of you by my side.



